Supplemental Material for\\Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/05_position_length_experiment.tex
Supplemental changes.

	Grouped bar charts are better computational perceivable than divided bar charts.} A grouped bar chart involves judging a position while a divided bar chart most likely (if not type 2) requires length judgements.

>>>>

	Grouped bar charts are better computational perceivable than divided bar charts. A grouped bar chart involves judging a position while a divided bar chart most likely (if not type 2) requires length judgements.

### 2018-03-31 PAPER/SUPPLEMENTAL/supplemental.tex
Supplemental changes.

%% indicate IEEE Member or Student Member in form indicated below
%\author{Daniel Haehn, \textit{Member, IEEE}, James Tompkin, and Hanspeter Pfister}
\author{Daniel Haehn, James Tompkin, and Hanspeter Pfister}
\authorfooter{
%% insert punctuation at end of each item
\item Daniel Haehn, and Hanspeter Pfister are with the Paulson School of Engineering and Applied Sciences at Harvard University. \\
E-mail: \{haehn,pfister\}@seas.harvard.edu.
%
\item James Tompkin is with the Thomas J. Watson Sr. Center for Information Technology at Brown University. \\E-mail: james\_tompkin@brown.edu.
}

@@

\begin{document}
\maketitle
%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.

%% the only exception to this rule is the \firstsection command
\begin{figure*}
\centering
This material contains several plots accompanying the main manuscript.
\end{figure*}
\clearpage
\begin{figure*}[t]
	\centering
	  \includegraphics[width=.8\linewidth]{error_inspection_new.pdf}
  \caption{\textbf{Error distributions.} Error distributions of our networks when decoding elementary perceptual tasks.}
	\label{fig:errors}
\end{figure*}

\begin{figure*}[t]
	\centering
	  \includegraphics[width=\linewidth]{cross_network_new.pdf}
  \caption{\textbf{Cross-network variability.} Our networks fail when the stimuli changes through translation or stroke width. The x-labels indicate the training configuration while the y-labels indicate the stimuli variation. Numbers represent MLAE.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.48\linewidth]{../gfx/figure1_slim_left.pdf}
	  \includegraphics[width=.48\linewidth]{../gfx/figure1_slim_right.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) for all generated stimuli and across all networks. The * indicates networks which use ImageNet weights instead of bein trained from scratch.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=\linewidth]{../gfx/figure1_boxplot_new.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) visualized as box plots.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure}[t]
	\centering
	  \includegraphics[width=\linewidth]{../gfx/figure3_mlae_better_all_AA.pdf}
  \caption{\textbf{Anti-aliasing.} We test whether anti-aliasing effects the performance of our networks on pie charts by measuring MLAE. The difference is not statistically significant ($F(1,30)=0.341,p>0.5$).}
	\label{fig:aa}
\end{figure}

@@

%\bibliographystyle{abbrv}
\bibliographystyle{abbrv-doi}
%\bibliographystyle{abbrv-doi-narrow}
%\bibliographystyle{abbrv-doi-hyperref}
%\bibliographystyle{abbrv-doi-hyperref-narrow}

\bibliography{../paper.bib}
\end{document}

>>>>

%% indicate IEEE Member or Student Member in form indicated below
%\author{Daniel Haehn, \textit{Member, IEEE}, James Tompkin, and Hanspeter Pfister}
\author{Daniel Haehn, James Tompkin, and Hanspeter Pfister}
\authorfooter{
%% insert punctuation at end of each item
\item Daniel Haehn, and Hanspeter Pfister are with the Paulson School of Engineering and Applied Sciences at Harvard University. \\
E-mail: \{haehn,pfister\}@seas.harvard.edu.
%
\item James Tompkin is with Brown University. \\E-mail: james\_tompkin@brown.edu.
}

@@

\begin{document}
\maketitle

We present several plots which contain complete results for the elementary perceptual task experiment, for which, given the number of experiments, the main paper presented only a selection. We report MLAE for all added parameters to the stimuli, rather than just the most complex parameterization as in the main paper (Figures~\ref{fig:epc_mlae} and \ref{fig:epc_mlae_boxplots}). From this, we see that performance is largely equal across parameters, showing that most networks have sufficient capacity for the given parameterizations.

We also report complete results for the cross-network variability experiment on the elementary perceptual task experiment (Figure \ref{fig:cross_network}). As in the main paper, this shows that our networks are not able to generalize to additional translation or stroke width parameters without representative training data.

Further, we show how the errors for each network are distributed, across elementary perceptual tasks and across different cross-validation splits (Figure~\ref{fig:errors}). Most errors are approximately normally distributed, though our CNN with less parameters (LeNet) and our MLP often have errors which are farther from a normal distribution, and show structure.

\section{Experiment: Anti-aliasing}
We also include an experimental result showing that, for our stimuli, adding anti-aliasing to the line generation was not important to the tested CNNs (Figure~\ref{fig:aa}).

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{../gfx/figure3_mlae_better_all_AA.pdf}
\caption{\textbf{Anti-aliasing.} We test whether anti-aliasing effects the performance of our networks on pie charts by measuring MLAE. The difference is not statistically significant ($F(1,30)=0.341,p>0.5$).}
\label{fig:aa}
\end{figure}

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.

%% the only exception to this rule is the \firstsection command

\begin{figure*}[p]
	\centering
		\includegraphics[width=.48\linewidth]{../gfx/figure1_slim_left.pdf}
	  \includegraphics[width=.48\linewidth]{../gfx/figure1_slim_right.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) for all generated stimuli and across all networks. The * indicates networks which use ImageNet weights instead of bein trained from scratch.}
	\label{fig:epc_mlae}
\end{figure*}

\begin{figure*}[p]
	\centering
		\includegraphics[width=\linewidth]{../gfx/figure1_boxplot_new.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) visualized as box plots.}
	\label{fig:epc_mlae_boxplots}
\end{figure*}

\begin{figure*}[p]
	\centering
	  \includegraphics[width=\linewidth]{cross_network_new.pdf}
  \caption{\textbf{Cross-network variability.} Our networks fail when the stimuli changes through translation or stroke width. The x-labels indicate the training configuration while the y-labels indicate the stimuli variation. Numbers represent MLAE.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[p]
	\centering
	  \includegraphics[width=.8\linewidth]{error_inspection_new.pdf}
  \caption{\textbf{Error distributions.} Error distributions of our networks when decoding elementary perceptual tasks.}
	\label{fig:errors}
\end{figure*}

@@

%\bibliographystyle{abbrv}
%\bibliographystyle{abbrv-doi}
%\bibliographystyle{abbrv-doi-narrow}
%\bibliographystyle{abbrv-doi-hyperref}
%\bibliographystyle{abbrv-doi-hyperref-narrow}

%\bibliography{../paper}
\end{document}
